---
title: "Offense"
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(readxl)
library(writexl)
library(stringr)
library(rstanarm)
library(dplyr)
```

```{r}
#| echo: false
#| message: false
#| warning: false
mls_data <- read.csv("mls-salaries-2007.csv")

```

### Plot for all forwards in MLS League in 2007
```{r}
#| echo: false
#| message: false
#| warning: false
mls_data |> 
  filter(position == "F") |> 
  select(position, base_salary, club, first_name, last_name) |> 
  ggplot(mapping = aes(x = position, 
                       y = base_salary, 
                       color = club)) + 
  geom_jitter() + 
  scale_y_continuous(labels=scales::dollar_format()) + 
  labs(title = "Soccer salaries earned for forward players in 2007", 
       x = "Position", 
       y = "Player Base Salary", 
       caption = "Source: Originally from MLS Union") + 
  theme_classic()
```
This data shows the spread of salaries for defenders in 2007. The colors show the clubs each player was in, and the highest player salary was around 2.5 million dollars. 

### Plot for average forward salary in 2007
```{r}
#| echo: false
#| message: false
#| warning: false
data<- mls_data |> 
                  filter(position == "F") |> 
                  reframe(position, salary = mean(base_salary))
data <- slice(data, 1)

data |> 
  ggplot(mapping = aes(x = position, 
                       y = salary, 
                       fill = position)) + 
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels=scales::dollar_format()) + 
  labs(title = "Average player salary earned for forward players in 2007", 
       x = "Position", 
       y = "Player Base Salary", 
       caption = "Source: Originally from MLS Union") +
  theme_classic()

```
This data shows a graph for the average salary a forward had in 2007. This was approximately $150,000, which is more than average for defensive positions.
